\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-04-11 eg6-letters/NIM/EG6_RTPC_NIM.tex
Add a paragraph of context in the calibration section

In this section we will detail the methods used to calibrate the drift speed,
drift paths and gains of the detector. Note that for drift speed and drift
path we use the symetry of the detector and ...

{\bf Don't we want to have description and quality of elastic event selection in here somewhere?}

@@

We measure the drift speed using tracks detected in the RTPC. In figure 
\ref{fig:RTPC_signals}, a typical $^{4}$He track is represented (in green). After 
it causes ionization in the drift region, the released electrons (in black) 
drift to the cylindrical detection plane under the effect of the electric field. The 
electrons released close to the cathode take the most time to reach the readout 
pads, but geometrical symmetry insures they always travel the same 
distance. By identifying the maximum TDC measured, we can infer the drift 
speed of the electrons in the RTPC.\\

>>>>

In this section we will detail the methods used to calibrate the drift speed,
drift paths and gains of the detector. Drift speed and paths were initially
calculated using the MAGBOLTZ~\cite{MAGBOLTZ} program, then refined using
data to account for variations of the run conditions. We still always assume 
cylindrical symmetry in the chamber for the calibration, such that none of
the parameters depend on the asimuthal angle $\phi$. The initial MAGBOLTZ
calibration was improved through several iterations of the
process described below, each iteration increasing the number of events 
properly reconstructed in the RTPC. The figures presented in this section
are the one obtained while performing the last iteration of this long 
calibration process.

@@

We determine the drift speed using tracks reconstructed in the RTPC. In figure 
\ref{fig:RTPC_signals}, a typical $^{4}$He track is represented (in green). After 
it causes ionization in the drift region, the released electrons (in black) 
drift to the cylindrical detection plane under the effect of the electric field. The 
electrons released close to the cathode take the most time to reach the readout 
pads, but geometrical symmetry insures they always travel the same 
distance. By identifying the maximum TDC measured, we can infer the drift 
speed of the electrons in the RTPC.\\
